Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-16 content/appendix.tex
proving other direction of lemma 8

\begin{lemma}\label{lem:sound3}
  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, $r\in R$ a receiver, and $d\in D$ a data-flow fact. Then
  \begin{equation}
    d\in M_F(p)(\varnothing)\iff\mpd(r)\ne\top_T\,.
  \end{equation}\mtodo{Prove other direction}
\end{lemma}
\begin{proof}
  We start by proving that if $d\in M_F(p)(\varnothing)$, then $\mpd(r)\ne\top_T$, by induction on the length of the execution trace.

@@

    For the other direction, we will prove that if $\mpd(r)\ne\top_T$, then $d\in M_F(p)(\varnothing)$.
\end{proof}

>>>>

\begin{lemma}\label{lem:sound3}
  Let $p=[\startmain,\,\dots,\,n]$ be a concrete execution path, $r\in R$ a receiver, and $d\in D$ a data-flow fact. Then
  \begin{equation}
    d\in M_F(p)(\varnothing)\iff\mpd(r)\ne\top_T\,.
  \end{equation}
\end{lemma}
\begin{proof}
  We start by proving that if $d\in M_F(p)(\varnothing)$, then $\mpd(r)\ne\top_T$, by induction on the length of the execution trace.

@@

    For the other direction, we need to show that if $\mpd(r)\ne\top_T$, then $d\in M_F(p)(\varnothing)$.

    The fact that $\mpd(r)\ne\top_T$ means that there exists a realizable path corresponding to the fact $d$ along path $p$, and, by definition, $d$ must be contained in $M_F(p)(\varnothing)$.\mtodo{Is this hand-wavy?}
\end{proof}
